The \project{unRAVE} catalog

### 2016-09-06 article/unrave.tex
Additions to GC plot including NGC1851 and to tex file

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} found 80 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 members of NGC~362. In addition to these systems, NGC~6752 and \stub{47~Tuc} were observed \citep{Kunder_2016}. For a detailed description of the cluster membership for NGC~5139, NGC~3201, and NGC~362 we refer the reader to \cite{Anguiano_2015}. The membership selection of the remaining clusters can be found in \cite{Kunder_2016}. \stub{check if this is the case in Kunder et al 2016.} We note here that we have not re-evaluated cluster membership as that is beyond the scope of the paper, however with the results presented here it is possible to study these systems in further detail.

In the top panel of Figure~\ref{fig:globular-cluster-HRD} we plot the spectroscopic H-R diagram for the members of these globular clusters. For comparison, in the bottom panel of Figure~\ref{fig:globular-cluster-HRD} we show the same as the top panel but for the RAVE DR4. In both panels isochrones, we have also plotted the PARSEC isochrones \citep{	
Bressan_2012} for comparison. The basic properties of the globular cluster used to generate the isochrones were sourced from Table 2 of \cite{Kunder_2016} and from the 2010 version of the Harris Globular Cluster Catalogue \citep{Harris_1996}.This figure indicates that for some stars in specific clusters clusters, namely NGC3201 and NGC362, are slightly offset from the isochrones most likely because the star's metallicity is significantly higher than the mean cluster metallicity. This could be a result of a combination of the inclusion of stars that are not cluster members but appeared to be consistent with the RAVE DR4 stellar parameters. In the remaining globular clusters the stars are consistent with the isochrones. In the case of NGC5139 ($\omega$ cen), it may be possible to pick out two of the several components that exist within that cluster.

@@

@@

>>>>

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 members of NGC~362. In addition to these systems, 12 stars thought to belong to NGC~1851 were found in the RAVE data in \cite{Kunder_2014} and 10 stars in NGC~6752 and XX stars in \stub{47~Tuc} were discussed in \citep{Kunder_2016}. For a detailed description of the cluster membership for NGC~5139, NGC~3201, and NGC~362 we refer the reader to \cite{Anguiano_2015}. The membership selection for NGC~1851 can be found in \citep{Kunder_2014} and for NGC~6752 and 47~Tuc can be found in \cite{Kunder_2016}. We note here that we have not re-evaluated cluster membership as that is beyond the scope of the paper, however with the results presented here it is possible to study these systems in further detail.

In the top panel of Figure~\ref{fig:globular-cluster-HRD} we plot the spectroscopic H-R diagram for the members of these globular clusters. For comparison, in the bottom panel of Figure~\ref{fig:globular-cluster-HRD} we show the same as the top panel but for the RAVE DR4. In both panels isochrones, we have also plotted the PARSEC isochrones \citep{	
Bressan_2012} for comparison. The basic properties of the globular cluster used to generate the isochrones were sourced from Table 2 of \cite{Kunder_2016}, \cite{Marin-Franch_2009}, and the 2010 version of the Harris Globular Cluster Catalogue \citep{Harris_1996}.This figure indicates that for some stars in specific clusters clusters, namely NGC3201 and NGC362, are slightly offset from the isochrones most likely because the star's metallicity is significantly higher than the mean cluster metallicity. This could be a result of a combination of the inclusion of stars that are not cluster members but appeared to be consistent with the RAVE DR4 stellar parameters. In the remaining globular clusters the stars are consistent with the isochrones. In the case of NGC5139 ($\omega$ cen), it may be possible to pick out two of the several components that exist within that cluster.

@@

\bibitem[Kunder et al.(2014)]{Kunder_2014} Kunder, A., Bono, G., Piffl, T., et al.\ 2014, \aap, 572, A30

@@

\bibitem[Mar{\'{\i}}n-Franch et al.(2009)]{Marin-Franch_2009} Mar{\'{\i}}n-Franch, A., Aparicio, A., Piotto, G., et al.\ 2009, \apj, 694, 1498
